The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
added to descriptions of graph 3-5

![Figure 1](../other/figures/figure1.png)
![Figure 5](../other/figures/figure5.png)
After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts. While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days. Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate at over 32.2 degrees Celsius has dropped tremendously while that of between 26.7-32.3 degrees Celsius remained consistent. However, it becomes evident that after the policy implementation, at similar ranges of 25-30 degrees Celsius and over 30 degrees Celsius produced a higher mortality rate. [figure 5]

@@

The next steps would be to find more recent data. As aforementioned, the datasets only extend until 2016 and to complete a long-term analysis, more recent Japanese energy data needs to be collected. Moreover, data from before and after other global nuclear incidents should be gathered and evalauted in comparison to Fukushima to evaluate whether the Japanese government's apporoach was the most optimal. Another step that can be taken to futher the analysis could be to explore more granular effects. For example, in addition to looking at how ambulance calls and heat strokes can be correlated and how increased temperature can cause higher mortality rates before and after the energy policy, other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.

>>>>

![Figure 1](../other/figures/figure1.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)
After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts. While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days. Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3]. In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted. To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy. Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et. al).

@@

The next steps would be to find more recent data. As aforementioned, the datasets only extend until 2016 and to complete a long-term analysis, more recent Japanese energy data needs to be collected. Moreover, data from before and after other global nuclear incidents should be gathered and evaluated in comparison to Fukushima to evaluate whether the Japanese government's approach was the most optimal. Another step that can be taken to further the analysis could be to explore more granular effects. For example, in addition to looking at how ambulance calls and heat strokes can be correlated and how increased temperature can cause higher mortality rates before and after the energy policy, other factors such as energy price variation and seasons or energy jobs and employment rates can be observed as well.
